---
title: "Replication of Hills 2009"
author: "Isaac Scheinfeld"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
---
# Networks

## Setup

First we import helper functions and configure RMarkdown.
```{r message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
```

We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.
```{r warning=FALSE}
# The "defintion" is the word, the "unilemma"" is the translation in English.

vocab <- make_vocab_dataframe(lang="English (American)",
                              lang_form = "WS",
                              lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition()
```

## Build Networks

Next, we construct networks following the example of Hills. Using vocabulary obtained by 30 months and the same MacRae features as Hills, we construct networks from perceptual and conceptual features. We consider only words for which some feature data is available (though not necessarily perceptual or conceptual), and track the number of features that generate each edge.

```{r message=FALSE}
perceptual_features = c("sound", "taste", "smell", "tactile", 
                           "visual-form_and_surface", "visual-motion", "visual-color")
conceptual_features = c("function")

full_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
                                feature_types = c(perceptual_features,
                                                  conceptual_features)) %>%
                  set.graph.attribute("type", "both")

perceptual_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
                                      feature_types = perceptual_features) %>%
                        set.graph.attribute("type", "perceptual")
conceptual_network <- feature_network(vocab, max_age = 30, shared_threshold = 1,
                                      feature_types = conceptual_features) %>%
                        set.graph.attribute("type", "conceptual")
```

## Visualize Networks
```{r out.width = '100%'}
dense_network <- perceptual_network
sparse_network <- perceptual_network %E>%
  filter(shared >= 2)

plot_network(dense_network)
plot_network(sparse_network)
```

# Clusters

Here I experiment with various clustering algorithms, which vary in whether they take weighting into account, whether they allow overlapping clusters, and various other properties.

## Clique Percolation - Unweighted, Overlapping

Clique percolation requires the choice of a parameter k, which is the size of the clique by which vertices must be connected to be considered contained in the same cluster. For this reason, vertices which are themselves not part of a k-clique are not included in a cluster.
```{r out.width = '100%'}
par(mfrow=c(1,2), mar=rep(1,4))
dense_clusters <- clique.community.opt(dense_network, 2)
sparse_clusters <- clique.community.opt(sparse_network, 3)

plot_network(dense_network, clusters = dense_clusters)
plot_network(sparse_network, clusters = sparse_clusters)
```

## Maximum Modularity - Unweighted
```{r}
dense_clusters <- cluster_fast_greedy(dense_network, weights = NULL)

# Plot
par(mfrow=c(1,2), mar=rep(1,4))
layout <-layout_with_fr(dense_network)
plot(dense_clusters, dense_network, layout=layout, vertex.label=NA, vertex.size=5,  edge.arrow.size=.2)

# # Change colors of nodes, polygons, and polygon borders
# new_cols <- c("white", "red", "black")[membership(sparse_clusters)]
# plot(sparse_clusters, sparse_network, col=new_cols, mark.border="black", mark.col=c("tan", "pink", "lightgray"), 
#     layout=layout, vertex.label=NA, vertex.size=5, edge.arrow.size=.2)
```

