---
title: "Comparison Word2Vec Analysis"
author: "Isaac Scheinfeld"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
---
# Preparation

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(purrr) # fp library
library(readr) # read text data files (csv, etc.)
library(ggplot2) # plotting
library(langcog) # useful things used by Language and Cognition Lab
library(dplyr) # for working with datafram-like objects
library(tidyr) # for data tidying
library(wordbankr) # access to wordbank data
library(stringr) # common string operations
library(broom) # converts R function outputs to tidy data frames
library(igraph) # network analysis and visualization
library(knitr) # general-purpose tool for dynamic report generation
library(kableExtra) # table formatting
library(lemon) # functions for working w/ ggplot2 and knitr extensions
library(tibble) # modern dataframes
library(tidygraph)
library(doParallel)
library(networkD3)
library(ForceAtlas2)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)
```

## Nouns

We begin with roughly the same data used by Hills. *(TODO fix, get same data)*

```{r warning=FALSE}
# We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.

full_vocab <- make_vocab_dataframe(lang="English (American)",
                                   lang_form = "WS",
                                   lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() %>%
  arrange(age) %>%            # keep first age for duplicates
  distinct(uni_lemma, .keep_all = TRUE) %>%
  select(uni_lemma, definition, age, category)
```

The initial vocabulary contains `r nrow(full_vocab)` (compared to Hills' 312).

## Perceptual & Conceptual Features

Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing  14 features for each noun.

```{r warning=FALSE, message=FALSE}
features <- load_features()
w2v <- load_w2v()

hills_vocab <- full_vocab %>%
  filter(age <= 30) %>%
  filter(uni_lemma %in% features$Concept) # filter to words with features

vocab <- hills_vocab %>%
  filter(uni_lemma %in% w2v$from | uni_lemma %in% w2v$to)
```

To begin our analysis, we only consider the words for which feature data are available, an overlap of `r nrow(hills_vocab)` in our data compared to Hills' 130. Then we filter the `r nrow(hills_vocab) - nrow(vocab)` words for which word2vec data is not available, for a final vocabulary of `r nrow(vocab)`.

## Build Network

Using vocabulary obtained by 30 months and the same McRae features as Hills, we construct a network with edge attributes for perceptual and conceptual features, and for word2vec similarity.

```{r message=FALSE}
# perceptual and conceptual McRae feature types
perceptual_features = c("sound", "taste", "smell", "tactile",
                        "visual-form_and_surface", "visual-motion", "visual-color")
conceptual_features = c("function")

# count shared features between words in vocabulary
perceptual_links <- make_feature_links(vocab = vocab,
                                       feature_types = perceptual_features) %>%
  rename(perceptual = shared)

conceptual_links <- make_feature_links(vocab = vocab,
                                       feature_types = conceptual_features) %>%
  rename(conceptual = shared)

# get word2vec distance between words in vocabulary
w2v_links <- make_w2v_links(vocab = vocab) #TODO still problem w/ vocab matching w2v data

links <- perceptual_links %>%
  full_join(conceptual_links, by=c("from", "to")) %>%
  full_join(w2v_links, by=c("from", "to"))

network <- graph_from_data_frame(links, vertices = vocab, directed = FALSE) %>%
  as_tbl_graph()
```

# Results

## The Network

First we generate a display layout for the network, based on the word2vec data.

```{r}
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

layout <- layout_network(network %E>% mutate(weights = w2v_similarity))

network <- network %N>%
  mutate(x = layout[,1]) %>%
  mutate(y = layout[,2])
```


We can examine the networks generated by filtering edges with a word2vec similarity threshold.

```{r out.width = '100%', dpi=300}
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

par(mfrow=c(2, 2), mar=c(2,0.4,0.8,0.4)) # row x col, column first

for (s in seq(0.35, 0.5, 0.05)) {
  plot_network(network %E>% filter(w2v_similarity > s),
               layout = layout,
               labels=TRUE,
               frame=FALSE,
               title=str_glue("Threshold = {s}"))
}

```

## Clustering algorithms

```{r out.width='100%', fig.asp=1/2, dpi=300}
# cluster_edge_betweenness - doesn't cluster reasonably, treats weights as distances?
# 
# cluster_infomap - returns one cluster
# 
# cluster_label_prop - returns one cluster
# 
# cluster_optimal - too computationally intensive for laptop, may not be possible (NP)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

par(mfrow=c(1, 2), mar=c(2,0.4,0.8,0.4)) # row x col, column first

feature_network <- network %E>%
  mutate_all(funs(replace(., is.na(.), 0))) %>%
  mutate(features = perceptual + conceptual) %>%
  filter(features > 0)

# cluster_fast_greedy
plot_network(network, layout = layout,
             clusters = cluster_fast_greedy(network,
                                            weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_fast_greedy(feature_network,
                                            weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)

# cluster_leading_eigen
plot_network(network, layout = layout,
             clusters = cluster_leading_eigen(network,
                                              weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_leading_eigen(feature_network,
                                              weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)

# cluster_louvain
plot_network(network, layout = layout,
             clusters = cluster_louvain(network,
                                        weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_louvain(feature_network,
                                        weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)

# cluster_spinglass
plot_network(network, layout = layout,
             clusters = cluster_spinglass(network,
                                          weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_spinglass(feature_network,
                                          weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)

# cluster_walktrap
plot_network(network, layout = layout,
             clusters = cluster_walktrap(network,
                                         weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_walktrap(feature_network,
                                         weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)
```

```{r out.width='100%', fig.asp=1/2, dpi=300}
# cluster_walktrap
for (age_limit in seq(16, 30, by=2)) {
  net_at_age <- network %N>% filter(age <= age_limit) %E>% mutate(weights = w2v_similarity)
  
  plot_network(net_at_age,
               clusters = cluster_walktrap(net_at_age,
                                           weights = E(net_at_age)$w2v_similarity)$membership,
               labels = TRUE,
               frame = TRUE)
}
```

```{r}
feature_net <- network %E>% mutate(weights = perceptual) %E>% filter(weights > 0) %N>% filter(!node_is_isolated())
feature_layout <- layout_network(feature_net)

feature_net <- feature_net %N>%
  mutate(x = feature_layout[,1]) %>%
  mutate(y = feature_layout[,2])


```

```{r out.width='100%', fig.asp=1/2, dpi=300}
# cluster_walktrap
for (age_limit in seq(16, 30, by=2)) {
  net_at_age <- feature_net %N>% filter(age <= age_limit) %E>% mutate(weights = perceptual)
  
  plot_network(net_at_age,
               clusters = cluster_walktrap(net_at_age,
                                           weights = E(net_at_age)$perceptual)$membership,
               labels = TRUE,
               frame = TRUE)
}
```
